Stochastic Variance-Reduced Policy Gradient

### 2018-02-09 svrpg.tex
typo

Figure \ref{fig:cartpole} compares SVRPG with G(PO)MDP on a continuous variant of the classical Cart-pole task, which is a 2D balancing task. Despite using more trajectories for each parameter,\todopirout{I do not understand this sentence} our algorithm shows faster convergence, which can be ascribed to the better quality of updates due to variance reduction.

>>>>

Figure \ref{fig:cartpole} compares SVRPG with G(PO)MDP on a continuous variant of the classical Cart-pole task, which is a 2D balancing task. {\color{blue}Despite using more trajectories for each parameter update}, our algorithm shows faster convergence, which can be ascribed to the better quality of updates due to variance reduction.
